---
title: "Github page"
output:
  html_document:
    theme: lumen
    highlight: tango
    toc: yes
    toc_position: right
    toc_float: yes
    smooth_scroll: false
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(lingtypology)
```

### Typology of Iconicity Patterns in Sign Languages

This page represents sign languages' preferences for iconicity patterns and iconicity bases in respect to different iconic signs.

Here is a link to download our dataset: [.csv](https://raw.githubusercontent.com/Pandaklez/Iconicity-in-Sign-Languages/master/annotated_data_new.csv)

### Window

```{r}
df <- read.csv("window.csv")
df$urls <- sapply(df$urls, function(x){paste(c("<video width='250' height='200' controls> <source src='", as.character(x), "' type='video/mp4'></video>"), sep = "", collapse = "")})
set.seed(4) # for having the same colors
m <- map.feature(languages = df$languages,
                 features = df$pattern,
                 stroke.features = df$base,
                 popup = df$urls,
                 title = df$word[1],
                 width = 500)
```

### Word 3

```{r}
map.feature("Adyghe")
```

### Word 4

```{r}
map.feature("Adyghe")
```

### Word 5

```{r}
map.feature("Adyghe")
```

### Word 6

```{r}
map.feature("Adyghe")
```

### Word 7

```{r}
map.feature("Adyghe")
```

### Word 8

```{r}
map.feature("Adyghe")
```

### Word 9

```{r}
map.feature("Adyghe")
```

### Word 10

```{r}
map.feature("Adyghe")
```

### Word 11

```{r}
map.feature("Adyghe")
```

### Word 12

```{r}
map.feature("Adyghe")
```

### Word 13

```{r}
map.feature("Adyghe")
```

### Word 14

```{r}
map.feature("Adyghe")
```

### Word 15

```{r}
map.feature("Adyghe")
```

### Word 16

```{r}
map.feature("Adyghe")
```

### Word 17

```{r}
map.feature("Adyghe")
```

### Word 1

```{r}
map.feature("Adyghe")
```

### Word 2

```{r}
map.feature("Adyghe")
```

### Word 3

```{r}
map.feature("Adyghe")
```

### Word 4

```{r}
map.feature("Adyghe")
```

### Word 5

```{r}
map.feature("Adyghe")
```

### Word 6

```{r}
map.feature("Adyghe")
```

### Word 7

```{r}
map.feature("Adyghe")
```

### Word 8

```{r}
map.feature("Adyghe")
```

### Word 9

```{r}
map.feature("Adyghe")
```

### Word 10

```{r}
map.feature("Adyghe")
```

### Word 11

```{r}
map.feature("Adyghe")
```

### Word 12

```{r}
map.feature("Adyghe")
```

### Word 13

```{r}
map.feature("Adyghe")
```

### Word 14

```{r}
map.feature("Adyghe")
```

### Word 15

```{r}
map.feature("Adyghe")
```

### Word 16

```{r}
map.feature("Adyghe")
```

### Word 17

```{r}
map.feature("Adyghe")
```
